---
title: "Amazon Prime"
author: "Leah Boger"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Amazon Prime Movies and TV
link to kaggle: https://www.kaggle.com/datasets/dgoenrique/amazon-prime-movies-and-tv-shows

```{r}
library(tidyverse)
titles <- read.csv("/Users/leahboger/Desktop/amazon prime/titles.csv")
credits <- read.csv("/Users/leahboger/Desktop/amazon prime/credits.csv")
```


Q1) Which shows/movies have the largest difference in imdb score vs tmdb score, and what is that difference?
A: Zone Drifter has the largest difference in scores (7.7 pt difference). After looking at the amount of votes/ popularity of the top five largest discrepancies, it seems that the larger discrepancies are very unpopular films, so there is most likely more variance in the ratings.
```{r}
titles %>% mutate(score_diff = abs(imdb_score - tmdb_score)) %>% arrange(-score_diff) %>% select(title, score_diff, imdb_score, imdb_votes, tmdb_score, tmdb_popularity) %>% head(5)
```

Q2) Create a graph to show how the average length of movies changed over time.
```{r}
library(plotly)
library(mdsr)
avg_time_per_year <- titles %>% filter(type == "MOVIE") %>% group_by(release_year) %>% summarize(avg_length = mean(runtime))

static_plot <- avg_time_per_year %>% ggplot(aes(x = release_year, y = avg_length)) + geom_line() + xlab("Release Year") + ylab("Average Movie Length")

ggplotly(static_plot)

```



Q3) Make a graph to explore a possible correlation between runtime and average rating(the average of the imdb and tmdb scores).
```{r}
#incorrect data point removal
titles %>% filter(runtime == 940) %>% select(title)
#after checking amazon.com, this movie is 93 minutes, below this data point will be fixed
titles %>% filter(runtime == 328) %>% select(title)
#after checking amazon.com, this movie is 88 minutes, below this data point will be fixed

corrected_outliers <- titles %>% mutate(runtime = case_when(title == "Once Bitten" & runtime == 940 ~ 93, title == "Custer's Last Stand" & runtime == 328 ~ 88, TRUE ~ runtime))




avg_rating <- corrected_outliers %>% mutate(avg_rating = (imdb_score + tmdb_score)/2) %>% select(type, avg_rating, runtime)

static_plot2 <- avg_rating %>% ggplot(aes(x = runtime, y = avg_rating)) + geom_point() + facet_wrap( ~ type) + geom_smooth() + ylab("Average Rating") + xlab("Runtime") + xlim(0,350)

ggplotly(static_plot2)



```

Q4) What actor has been in the most TV shows + Movies and which TV shows and movies were they in? What director?
A: The actor in the most media is George 'Gabby' Hayes, being in 53 movies. The Director in the most media is Joesph Kane, working on 45 movies
```{r}
#actor
top_actor <- credits %>% filter(role == "ACTOR") %>% group_by(person_id, name) %>% summarize(num_film = length(unique(id))) %>% arrange(-num_film) %>% head(1) %>% pull(person_id)

top_actor_name <- credits %>% filter(role == "ACTOR") %>% group_by(person_id, name) %>% summarize(num_film = length(unique(id))) %>% arrange(-num_film) %>% head(1) %>% pull(name)

ls_films_w_actor <- credits %>% filter(person_id == top_actor) %>% group_by(id) %>% summarize(id = id)

filmsact <- ls_films_w_actor %>% left_join(titles, by = c("id")) %>% select(title, type, seasons, imdb_score)

#top actor
top_actor_name
filmsact 
nrow(filmsact)
unique(filmsact$type)

#director
top_director <- credits %>% filter(role == "DIRECTOR") %>% group_by(person_id, name) %>% summarize(num_film = length(unique(id))) %>% arrange(-num_film) %>% head(1) %>% pull(person_id)

top_director_name <- credits %>% filter(role == "DIRECTOR") %>% group_by(person_id, name) %>% summarize(num_film = length(unique(id))) %>% arrange(-num_film) %>% head(1) %>% pull(name)

ls_films_w_director <- credits %>% filter(person_id == top_director) %>% group_by(id) %>% summarize(id = id)

filmsdir <- ls_films_w_director %>% left_join(titles, by = c("id")) %>% select(title, type, seasons, imdb_score)

#top director

top_director_name
filmsdir
nrow(filmsdir)
unique(filmsdir$type)




```


Q5) Graph the number of productions a person worked on versus the average imdb score those productions have. Facet by role in the media.  
```{r}

number_films <- credits %>% group_by(person_id) %>% summarize(num_film = length(unique(id)))


person_w_id <- credits %>% group_by(person_id, id, role) %>% summarize(id = id) %>% select(person_id, id, role)


imdb_w_filmnum <- person_w_id %>% left_join(titles, by = c("id")) %>% group_by(person_id, role) %>% summarize(avg_imdb = mean(imdb_score)) %>% left_join(number_films, by = c("person_id"))


imdb_w_filmnum %>% ggplot(aes(x= num_film, y = avg_imdb)) + geom_point() + facet_wrap( ~ role) + xlab("Number of Productions Worked On") + ylab("Average IMDB Score")

```




